Clustering of Distributions on 1-Dimensional Manifolds

### 2021-09-01 scratch/distributions-on-1d-manifolds.Rmd
proof sketch for general case
typo

## Setup

@@

## Theory

@@

### Uniform case

@@

### Beta case

### General case

@@

Which becomes $1 - C P(n) e^{-n}$ for some $C > 0$ and $P(n)$ is a polynomial of $n$. This goes to 0 as $n \to \infty$, giving us the result $D_i \stackrel{p}{\to} 0$.

## Computational Results

>>>>

# Setup

@@

# Theory

@@

## Uniform case

@@

## General case

### Proof sketch that $P(D_i \leq \delta) \to 1$

@@

Which becomes $1 - C P(n) \delta^{n}$ for some $C > 0$ and $P(n)$ is a polynomial of $n$, giving us the desired result $D_i \stackrel{p}{\to} 0$.

# Computational Results

### 2021-09-01 scratch/distributions-on-1d-manifolds.tex
proof sketch for general case
typo

\hypertarget{setup}{%
\subsection{Setup}\label{setup}}

@@

\hypertarget{theory}{%
\subsection{Theory}\label{theory}}

@@

\hypertarget{uniform-case}{%
\subsubsection{Uniform case}\label{uniform-case}}

@@

\hypertarget{general-case}{%
\subsubsection{General case}\label{general-case}}

\hypertarget{proof-sketch-that-pd_i-leq-delta-to-1}{%
\paragraph{\texorpdfstring{Proof sketch that
\(P(D_i \leq \delta) \to 1\)}{Proof sketch that P(D\_i \textbackslash leq \textbackslash delta) \textbackslash to 1}}\label{proof-sketch-that-pd_i-leq-delta-to-1}}

@@

Which becomes \(1 - C P(n) \delta^{n}\) for some \(C > 0\) and \(P(n)\)
is a polynomial of \(n\). This goes to 0 as \(n \to \infty\), giving us
the result \(D_i \stackrel{p}{\to} 0\).

\hypertarget{computational-results}{%
\subsection{Computational Results}\label{computational-results}}

>>>>

\hypertarget{setup}{%
\section{Setup}\label{setup}}

@@

\hypertarget{theory}{%
\section{Theory}\label{theory}}

@@

\hypertarget{uniform-case}{%
\subsection{Uniform case}\label{uniform-case}}

@@

\hypertarget{general-case}{%
\subsection{General case}\label{general-case}}

\hypertarget{proof-sketch-that-pd_i-leq-delta-to-1}{%
\subsubsection{\texorpdfstring{Proof sketch that
\(P(D_i \leq \delta) \to 1\)}{Proof sketch that P(D\_i \textbackslash leq \textbackslash delta) \textbackslash to 1}}\label{proof-sketch-that-pd_i-leq-delta-to-1}}

@@

Which becomes \(1 - C P(n) \delta^{n}\) for some \(C > 0\) and \(P(n)\)
is a polynomial of \(n\), giving us the desired result
\(D_i \stackrel{p}{\to} 0\).

\hypertarget{computational-results}{%
\section{Computational Results}\label{computational-results}}
